---
title: "A reproducibility study of structural and institutional determinants of influence and reputation"
author: "Devin Khosla, Jenny Liu, & Jui Nerurkar"
date: "12/16/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("network")
library("sna")
library("ergm")
library("tergm")
library("texreg")
library("xergm")
```

### Introduction
(give background as to what we are doing )
For this project we are reproducing results from Ingold and Leifeld (2016), titled 'Structural and Institutional Determinants of Influence and Reputation: A Comparison of Collaborative and Adversarial Policy Networks in Decision Making and Implementation` from the Journal of Public Administration Research and Theory. T 

(what are the authors proposing)

### Data
(describe the data we have)


### Visuals 
(make some plots of the networks)



### Models 
(code and explain what's going on and what the covariates explain etc and how that relates to the research question proposing)

```{r}
clim1.rep <- network(as.matrix(read.csv2("data/input/climate9500-rep.csv", row.names = 1, header = TRUE)))
# influence reputation network
clim1.collab <- network(as.matrix(read.csv2("data/input/climate9500-collab.csv", row.names = 1, header = TRUE)))  
# collaboration network
set.vertex.attribute(clim1.rep, "bc-perc", betweenness(clim1.collab, rescale = TRUE))  
# betweenness centrality as a vertex attribute
clim1.dm <- read.csv2("data/input/climate9500-dm.csv", row.names = 1, header = TRUE)
set.vertex.attribute(clim1.rep, "dm", clim1.dm$dm)  # decision-maker?
set.vertex.attribute(clim1.rep, "odeg-rep", degree(clim1.rep, cmode = "outdegree"))  
# outdegree centrality as a vertex attribute
com1 <- read.csv2("data/input/climate9500-committee.csv", row.names = 1, header = TRUE)
set.vertex.attribute(clim1.rep, "committees", rowSums(com1))
# number of committee memberships as a vertex attribute
```

```{r, message=FALSE}
climate1 <- ergm(clim1.rep ~ 
    edges + 
    cyclicalties + 
    transitiveties + 
    mutual + 
    nodeocov("odeg-rep") + 
    edgecov(clim1.collab) + 
    nodeicov("bc-perc") + 
    nodeifactor("dm") + 
    nodeicov("committees"), 
    control = control.ergm(seed = 12345)
) 
summary(climate1)
```

```{r, message=FALSE}
clim2.rep <- network(as.matrix(read.csv2("data/input/climate0205-rep.csv", row.names = 1, header = TRUE)))
# influence reputation network
clim2.collab <- network(as.matrix(read.csv2("data/input/climate0205-collab.csv", row.names = 1, header = TRUE)))
# collaboration network
set.vertex.attribute(clim2.rep, "bc-perc-2", 100 * betweenness(clim2.collab, rescale = TRUE))  
# betweenness centrality as a vertex attribute
clim2.dm <- read.csv2("data/input/climate0205-dm.csv", row.names = 1, header = TRUE)
set.vertex.attribute(clim2.rep, "dm", clim2.dm$dm)  # decision-maker?
set.vertex.attribute(clim2.rep, "odeg-rep", degree(clim2.rep, cmode = "outdegree"))  
# outdegree centrality as a vertex attribute
com2 <- read.csv2("data/input/climate0205-committee.csv", row.names = 1, header = TRUE)
set.vertex.attribute(clim2.rep, "committees-2", rowSums(com2))
# number of committee memberships as a vertex attribute
```

```{r, message=FALSE}
climate2 <- ergm(clim2.rep ~ 
    edges + 
    cyclicalties + 
    transitiveties + 
    mutual + 
    nodeocov("odeg-rep") + 
    edgecov(clim2.collab) + 
    nodeicov("bc-perc-2") + 
    nodeifactor("dm") + 
    nodeicov("committees-2"), 
    control = control.ergm(seed = 12345)
)
summary(climate2)
```

### Explore latent space models



### What we've learned 






